---
title: "Asynchronous Usage with kucoin"
author: "Dereck Mezquita"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Asynchronous Usage with kucoin}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  results = "hold",
  comment = "#>"
)

box::use(
  kucoin[KucoinMarketData, KucoinTrading, KucoinAccount, get_api_keys],
  coro[async, await],
  later[run_now, loop_empty],
  promises[then, catch, promise_all, promise_resolve]
)

box::use(../tests/testthat/mock_router[mock_router])
box::use(../tests/testthat/mockery[
  mock_response, mock_ticker_data, mock_eth_ticker_data
])

KEYS <- get_api_keys(
  api_key = "fake-key",
  api_secret = "fake-secret",
  api_passphrase = "fake-passphrase"
)
BASE <- "https://api.kucoin.com"

# Counter for ticker alternation (BTC / ETH in sequential & parallel examples)
.mock_state <- new.env(parent = emptyenv())
.mock_state$ticker_calls <- 0L

# Wrap shared router — override ticker to alternate BTC / ETH
options(httr2_mock = function(req) {
  if (grepl("market/orderbook/level1", req$url)) {
    .mock_state$ticker_calls <- .mock_state$ticker_calls + 1L
    data <- if (.mock_state$ticker_calls %% 2L == 1L) {
      mock_ticker_data()
    } else {
      mock_eth_ticker_data()
    }
    return(mock_response(data))
  }
  return(mock_router(req))
})
```

Every R6 class in `kucoin` accepts an `async = TRUE` flag at construction.
When enabled, all methods return `promises::promise` objects instead of
direct values. This vignette shows how to consume those promises with
`coro::async`/`await` and `later::run_now`.

## Why Async?

Synchronous HTTP blocks the R session while waiting for a reply.
Asynchronous mode lets you fire off multiple requests and process results
as they arrive — useful for bots that poll several endpoints or place
orders in parallel.

## Setup

```{r load}
box::use(
  kucoin[KucoinMarketData, KucoinTrading, KucoinAccount, get_api_keys],
  coro[async, await],
  later[run_now, loop_empty],
  promises[then, catch, promise_all, promise_resolve]
)

keys <- get_api_keys(
  api_key = "your-api-key",
  api_secret = "your-api-secret",
  api_passphrase = "your-api-passphrase"
)
```

```{r keys-hidden, echo = FALSE}
keys <- KEYS
base <- BASE
```

> **Event loop**: R does not have a built-in event loop like Node.js or
> Python's `asyncio`. Promises only resolve when the event loop ticks via
> `later::run_now()`. In scripts and vignettes, drain the loop with
> `while (!loop_empty()) run_now()`. In **Shiny** apps the event loop runs
> automatically.

---

## Basic Async: `coro::async` + `await`

The most ergonomic way to work with promises in R is `coro::async`, which
lets you write code that *looks* synchronous but runs asynchronously under
the hood — just like TypeScript's `async`/`await`.

```{r async-basic}
market <- KucoinMarketData$new(async = TRUE)
```

```{r async-basic-hidden, echo = FALSE}
market <- KucoinMarketData$new(keys = keys, base_url = base, async = TRUE)
```

```{r}
get_stats <- async(function() {
  stats <- await(market$get_24hr_stats(symbol = "BTC-USDT"))
  return(stats)
})

get_stats()
while (!loop_empty()) {
  run_now()
}
```

> **Key pattern**: define an `async` function, `await` each API call,
> return the result. Drain the event loop with `while (!loop_empty()) run_now()`.

---

## Sequential Async: Multiple `await` Calls

Chain several awaited calls in sequence — each one resolves before the
next begins, just like `await` in TypeScript:

```{r async-sequential}
results <- NULL

fetch_tickers <- async(function() {
  btc <- await(market$get_ticker(symbol = "BTC-USDT"))
  eth <- await(market$get_ticker(symbol = "ETH-USDT"))
  results <<- list(btc = btc, eth = eth)
})

fetch_tickers()
while (!loop_empty()) {
  run_now()
}
results$btc
results$eth
```

---

## Concurrent Requests with `promise_all`

When requests are independent, fire them simultaneously and collect all
results at once — the async equivalent of `Promise.all()` in TypeScript:

```{r async-parallel}
results <- NULL

fetch_parallel <- async(function() {
  # Launch both requests concurrently — no await yet, just collect promises
  btc_promise <- market$get_ticker(symbol = "BTC-USDT")
  eth_promise <- market$get_ticker(symbol = "ETH-USDT")
  # Await them together — like Promise.all([btc, eth])
  res <- await(promise_all(btc = btc_promise, eth = eth_promise))
  results <<- res
})

fetch_parallel()
while (!loop_empty()) {
  run_now()
}
results$btc
results$eth
```

---

## Promise Chaining with `then` / `catch`

If you prefer the promise-pipeline style (common in JavaScript), use
`then` and `catch`:

```{r promise-chain}
account <- KucoinAccount$new(async = TRUE)
```

```{r promise-chain-hidden, echo = FALSE}
account <- KucoinAccount$new(keys = keys, base_url = base, async = TRUE)
```

```{r}
chain_result <- NULL

account$get_summary() |>
  then(function(summary) {
    chain_result <<- summary
  }) |>
  catch(function(err) {
    message("Error: ", conditionMessage(err))
  })

while (!loop_empty()) {
  run_now()
}
chain_result
```

---

## Async Trading Example

Place a test order and immediately query open orders — sequential
`await` keeps the flow readable:

```{r async-trading}
trading <- KucoinTrading$new(async = TRUE)
```

```{r async-trading-hidden, echo = FALSE}
trading <- KucoinTrading$new(keys = keys, base_url = base, async = TRUE)
```

```{r}
results <- NULL

place_and_check <- async(function() {
  # Place a test order
  order <- await(trading$add_order_test(
    type = "limit",
    symbol = "BTC-USDT",
    side = "buy",
    price = "50000",
    size = "0.0001"
  ))

  # Query open orders
  open <- await(trading$get_open_orders(symbol = "BTC-USDT"))

  results <<- list(order = order, open = open)
})

place_and_check()
while (!loop_empty()) {
  run_now()
}
results$order
results$open
```

---

## Error Handling with `tryCatch`

Inside `async` functions, you can use `tryCatch` around `await` calls
for structured error handling — just like `try`/`catch` in TypeScript:

```{r async-error-handling, eval = FALSE}
safe_fetch <- async(function() {
  result <- tryCatch(
    await(market$get_ticker(symbol = "INVALID-PAIR")),
    error = function(e) {
      message("Caught error: ", conditionMessage(e))
      return(NULL)
    }
  )
  return(result)
})

safe_fetch()
while (!loop_empty()) {
  run_now()
}
```

---

## Running the Event Loop

The critical piece of async R is the **event loop**. Promises do not
resolve until the event loop ticks. In an interactive session or Shiny app,
the event loop runs automatically. In scripts or vignettes, you must drive
it manually.

```r
# Idiomatic event loop drain
while (!later::loop_empty()) {
  later::run_now()
}
```

Or with a timeout guard:

```r
deadline <- lubridate::now() + 30 # 30-second timeout
while (!later::loop_empty() && lubridate::now() < deadline) {
  later::run_now(timeoutSecs = 0.1)
}
```

In **Shiny** applications, the event loop is managed for you — simply
return promises from reactive expressions and Shiny handles resolution.

For bots or long-running processes, use the **Scheduler / Looper** pattern
(see package README) where `later` drives the loop automatically.

---

## `coro::await` Cheat Sheet

| Pattern | Works? | Notes |
|---------|--------|-------|
| `x <- await(promise)` | Yes | Standard pattern |
| `x <- await(obj$method(arg))` | Yes | Await wrapping a call is fine |
| `await(promise)` (bare, no assignment) | Yes | Side-effect only |
| `await` inside loops/if/tryCatch | Yes | Full control flow support |
| `x <<- await(promise)` | **No** | `<<-` not supported by coro |
| `f(await(promise))` | **No** | Nested inside function args |

> **Rule of thumb**: `await()` must appear as the RHS of a `<-` or as a
> bare statement — never inside another expression. Return values from
> the async function and extract them via `then()` or the `<<-` pattern
> outside the async body.

---

## Choosing Sync vs Async

| Scenario | Recommendation |
|----------|---------------|
| Interactive exploration | **Sync** — simpler, results print immediately |
| Scripts fetching one endpoint | **Sync** — no event loop needed |
| Bots polling multiple symbols | **Async** — concurrent requests reduce latency |
| Shiny dashboards | **Async** — keeps the UI responsive |
| Bulk data downloads | Use `kucoin_backfill_klines()` (sync, handles batching internally) |

---

## Next Steps

- See `vignette("getting-started")` for a full tour of all spot classes in sync mode.
- See `vignette("margin-trading")` for margin trading, short selling, and lending.
- See `vignette("futures-trading")` for perpetual futures contracts.
- Browse the [pkgdown site](https://dereckscompany.github.io/kucoin/) for full method documentation.
