---
title: "Data shapes and the one-row-per-entity convention"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Data shapes and the one-row-per-entity convention}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, purl = FALSE}
# All example chunks below carry `purl = FALSE` individually so that
# `R CMD check`'s vignette-tangling step does not extract them as
# runnable R code (they reference placeholder identifiers like
# `sub_user_id`, `order_id`, and `depth`). Setting `purl` here in
# `opts_chunk$set()` does NOT work — `knitr::purl()` does a static
# extraction and never evaluates this setup chunk, so the per-chunk
# `purl = FALSE` on each example is what actually skips them.
knitr::opts_chunk$set(eval = FALSE, collapse = TRUE, comment = "#>")
```

## The rule

Every `kucoin` method that returns nested API data follows one rule:

> **Identify the entity for the endpoint, and return one row per entity.**

A trade gets a row. An order gets a row. An asset balance gets a row. A
candle gets a row. Anything nested under the entity becomes a flat column
on the same row or an additional row on a different axis — **never a list
column**.

The same rule applies in the sister `alpaca` and `binance` packages, so
that switching between exchanges does not mean switching mental models of
how the data looks.

## The five shape treatments

There are five shapes a nested API field can take, and five treatments. A
few endpoints use two treatments together when their nesting has two
layers.

### Treatment A — `;` collapse for arrays of plain strings

When a field is an array of short, plain string values (codes, tags,
permissions) and the user mostly filters by them, collapse with `;` into a
single character column. Filter with `grepl`, recover the original vector
with `strsplit(x, ";", fixed = TRUE)[[1]]`.

The package ships a shared helper `collapse_string_array_fields(x,
fields)` that does this (NA-safe; emits a once-per-session warning if any
value contains a literal `;`).

### Treatment B — Long format for arrays of objects

When the array elements are themselves records (each has multiple fields),
explode to one row per element with the parent fields replicated. Add a
1-indexed position column where order matters.

```{r, purl = FALSE}
# `KucoinSubAccount::get_detail_balance()` returns one row per (sub-account
# × wallet bucket × asset). The sub-account-level fields (`sub_user_id`,
# `sub_name`, `account_type`) are replicated on each row.
sub <- KucoinSubAccount$new()
bal <- sub$get_detail_balance(sub_user_id)
bal[account_type == "trade", .(currency, balance, available, holds)]
```

```{r, purl = FALSE}
# `KucoinOcoOrders::get_order_detail_by_id()` explodes the `orders` array
# into `sub_order_*` columns — one row per child leg.
oco <- KucoinOcoOrders$new()
detail <- oco$get_order_detail_by_id(order_id)
detail[, .(order_id, sub_order_id, sub_order_side, sub_order_price)]
```

**Empty arrays**: KuCoin's Treatment B parsers don't know every
possible child field up-front (some sub-orders carry `stopPrice`, others
don't), so they don't synthesise an `NA`-filled `<noun>_*` schema when
the array is empty. `KucoinOcoOrders::get_order_detail_by_id()` with no
sub-orders returns just the parent columns; cancel parsers with an empty
`cancelledOrderIds` return a zero-row table. Defensive callers should
check `<noun>_*` columns with `"sub_order_id" %in% names(dt)` rather
than assuming they're always present.

### Treatment C — Wide prefix for fixed-schema nested objects

When the field is a single nested object with a known fixed key set,
flatten it to `parent_child` columns.

```{r, purl = FALSE}
# `KucoinAccount::get_isolated_margin_account()` flattens the nested
# `baseAsset` / `quoteAsset` per-pair objects into wide columns.
acct <- KucoinAccount$new()
iso <- acct$get_isolated_margin_account()
iso[, .(symbol, base_asset_currency, base_asset_borrow_enabled,
        quote_asset_currency, quote_asset_borrow_enabled)]
```

### Treatment D — Re-route to a sibling method

When a response bundles a collection that doesn't fit the per-entity row
of the calling endpoint — typically heterogeneous siblings (e.g. an
account-level summary bundled with per-asset rows) — the parser keeps the
rows for the entity the method names, and the rest is exposed via a
dedicated sibling method. Every method still returns one `data.table`; no
data is lost.

KuCoin uses this less frequently than `binance` because the KuCoin REST
API tends to namespace different entities to different endpoints already.

### Treatment E — JSON string for dynamic-key or array-of-array objects

When a nested object has dynamic keys (different products have different
key sets) or is an array of arrays where the inner grouping carries
semantic meaning, neither `;`-collapse nor wide-prefix preserves the
structure. Serialise the whole field as a JSON string; recover with
`jsonlite::fromJSON`.

## Two cross-cutting rules

These apply to every shape treatment:

1. **Empty / null array → `NA_character_`** (no list cells). An order
   with no fills returns `fill_id = NA`, not `fill_id = list()`.
2. **Empty response → empty `data.table`** (no synthetic stub rows).
   `KucoinTrading::cancel_all()` with no open orders returns a zero-row
   table, not a 1-row `(symbol, status = "cancelled")` fabrication. The
   absence of an error is the success signal.

## Why this shape works for `data.table`

`data.table` is fast and ergonomic on rectangular long-format data. List
columns make filtering, grouping, joining, and writing to disk awkward.
The convention above is what lets you write:

```{r, purl = FALSE}
# Top 5 highest-priced asks in the book
depth[side == "ask"][order(-price)][1:5]

# All BTC-USDT orders that filled at > 50k
orders <- KucoinTrading$new()$get_all_orders(query = list(symbol = "BTC-USDT"))
orders[as.numeric(deal_funds) > 50000]
```

…without escape hatches into `lapply` over hidden lists.

## See also

- `vignette("getting-started", package = "kucoin")` — the package tour.
- `vignette("async-usage", package = "kucoin")` — using the same methods
  with `async = TRUE`.
- The sister `alpaca` and `binance` packages — same convention applied to
  different exchanges. `binance`'s `vignette("data-shapes")` has a fuller
  per-class catalogue if you want to see every method's shape in one
  place.
