---
title: "Futures Trading with kucoin"
author: "Dereck Mezquita"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Futures Trading with kucoin}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  results = "hold",
  comment = "#>"
)

box::use(
  kucoin[
    KucoinFuturesMarketData, KucoinFuturesTrading, KucoinFuturesAccount,
    get_api_keys, get_futures_base_url
  ]
)

box::use(../tests/testthat/mock_router[mock_router])

KEYS <- get_api_keys(
  api_key = "fake-key",
  api_secret = "fake-secret",
  api_passphrase = "fake-passphrase"
)
BASE <- "https://api-futures.kucoin.com"

options(httr2_mock = mock_router)
```

This vignette covers KuCoin Futures trading using the `kucoin` package.
Futures contracts let you trade with leverage — amplifying both gains and
losses — on perpetual contracts like XBTUSDTM (BTC) and ETHUSDTM (ETH).

## Overview

The package provides three classes for futures operations:

| Class | Purpose |
|-------|---------|
| `KucoinFuturesMarketData` | Contract specs, tickers, orderbooks, klines, funding rates |
| `KucoinFuturesTrading` | Place, cancel, and query futures orders |
| `KucoinFuturesAccount` | Positions, margin, leverage, risk limits |

All futures classes use a separate base URL (`https://api-futures.kucoin.com`)
but share the same API key credentials as spot trading.

## Setup

```{r load}
box::use(
  kucoin[
    KucoinFuturesMarketData, KucoinFuturesTrading, KucoinFuturesAccount,
    get_api_keys
  ]
)

keys <- get_api_keys(
  api_key = "your-api-key",
  api_secret = "your-api-secret",
  api_passphrase = "your-api-passphrase"
)

market <- KucoinFuturesMarketData$new(keys = keys)
trading <- KucoinFuturesTrading$new(keys = keys)
account <- KucoinFuturesAccount$new(keys = keys)
```

```{r keys, echo = FALSE}
keys <- KEYS
base <- BASE
market <- KucoinFuturesMarketData$new(keys = keys, base_url = base)
trading <- KucoinFuturesTrading$new(keys = keys, base_url = base)
account <- KucoinFuturesAccount$new(keys = keys, base_url = base)
```

---

## Market Data

### Contract Details

Query the specification of a futures contract — lot sizes, tick sizes,
leverage limits, and fee rates:

```{r contract}
contract <- market$get_contract("XBTUSDTM")
contract[, .(symbol, max_leverage, tick_size, maker_fee_rate, taker_fee_rate)]
```

### All Active Contracts

```{r all-contracts}
contracts <- market$get_all_contracts()
contracts[, .(symbol, status)]
```

### Ticker

Real-time price and best bid/ask for a single contract:

```{r ticker}
ticker <- market$get_ticker("XBTUSDTM")
ticker[, .(symbol, price, best_bid_price, best_ask_price, ts)]
```

### All Tickers

```{r all-tickers}
tickers <- market$get_all_tickers()
tickers[, .(symbol, price, ts)]
```

### Orderbook

The partial orderbook returns the top 20 or 100 price levels:

```{r orderbook}
ob <- market$get_part_orderbook("XBTUSDTM", size = 20)
ob
```

### Trade History

```{r trades}
trades <- market$get_trade_history("XBTUSDTM")
trades[, .(side, price, size, ts)]
```

### Klines (Candlesticks)

Retrieve historical OHLCV data. Granularity is in minutes:

```{r klines}
klines <- market$get_klines("XBTUSDTM", granularity = 60)
klines
```

### Mark Price

The mark price is used for liquidation calculations and PNL:

```{r mark-price}
mark <- market$get_mark_price("XBTUSDTM")
mark
```

### Funding Rate

Perpetual futures settle funding every 8 hours. Positive rates mean longs
pay shorts; negative means shorts pay longs:

```{r funding-rate}
rate <- market$get_funding_rate("XBTUSDTM")
rate
```

### Server Time and Status

```{r server}
market$get_server_time()
market$get_service_status()
```

---

## Trading

All trading methods require API keys with **Futures trading permission**
enabled on KuCoin.

### Place an Order (Dry Run)

Use `add_order_test()` to validate parameters without placing a real order:

```{r order-test}
result <- trading$add_order_test(
  clientOid = "my-test-001",
  symbol = "XBTUSDTM",
  side = "buy",
  type = "limit",
  leverage = 5,
  size = 1,
  price = "98000"
)
result
```

### Place a Real Order

```{r order, eval = FALSE}
# Market order — no price needed
order <- trading$add_order(
  clientOid = "my-market-001",
  symbol = "XBTUSDTM",
  side = "buy",
  type = "market",
  leverage = 10,
  size = 1
)

# Limit order
order <- trading$add_order(
  clientOid = "my-limit-001",
  symbol = "XBTUSDTM",
  side = "buy",
  type = "limit",
  leverage = 5,
  size = 1,
  price = "95000",
  timeInForce = "GTC"
)
```

### Cancel Orders

```{r cancel, eval = FALSE}
# Cancel by system order ID
trading$cancel_order_by_id("order-id-here")

# Cancel by client order ID
trading$cancel_order_by_client_oid("my-limit-001", symbol = "XBTUSDTM")

# Cancel all orders for a symbol
trading$cancel_all(symbol = "XBTUSDTM")

# Cancel all stop orders
trading$cancel_all_stop_orders(symbol = "XBTUSDTM")
```

### Query Orders

```{r query-orders, eval = FALSE}
# Get a specific order
order <- trading$get_order_by_id("order-id")

# Get open orders
open <- trading$get_order_list(query = list(status = "active"))

# Get recent closed orders
closed <- trading$get_recent_closed_orders(symbol = "XBTUSDTM")
```

### Fills (Trade History)

```{r fills, eval = FALSE}
# All fills
fills <- trading$get_fills(query = list(symbol = "XBTUSDTM"))

# Recent fills (last 24h)
recent <- trading$get_recent_fills(symbol = "XBTUSDTM")
```

### Dead Connection Protection (DCP)

A dead-man's switch that auto-cancels orders if your bot stops sending
heartbeats:

```{r dcp}
# Set DCP with 5-second timeout
trading$set_dcp(timeout = 5)

# Check current DCP settings
trading$get_dcp()
```

---

## Account and Positions

### Account Overview

```{r account-overview}
overview <- account$get_account_overview(currency = "USDT")
overview[, .(account_equity, available_balance, unrealised_pnl, currency)]
```

### Positions

```{r positions}
# All open positions
positions <- account$get_positions()
positions[, .(symbol, current_qty, avg_entry_price, unrealised_pnl, margin_mode)]
```

### Position History

```{r position-history}
history <- account$get_positions_history()
history
```

### Margin Mode

Switch between isolated and cross margin:

```{r margin-mode}
# Check current mode
account$get_margin_mode("XBTUSDTM")
```

```{r set-margin, eval = FALSE}
# Switch to cross margin
account$set_margin_mode("XBTUSDTM", "CROSS")
```

### Leverage

```{r leverage}
account$get_cross_margin_leverage("XBTUSDTM")
```

```{r set-leverage, eval = FALSE}
account$set_cross_margin_leverage("XBTUSDTM", 10)
```

### Risk Limits

Each contract has tiered risk limits that reduce maximum leverage as
position size increases:

```{r risk-limits}
limits <- account$get_risk_limit("XBTUSDTM")
limits[, .(level, max_leverage, max_risk_limit, initial_margin)]
```

### Funding Fee History

Track funding fees you've paid or received:

```{r funding-history}
funding <- account$get_funding_history("XBTUSDTM")
funding
```

---

## Method Reference

### KucoinFuturesMarketData

| Method | Description |
|--------|-------------|
| `get_contract()` | Single contract specification |
| `get_all_contracts()` | All active contracts |
| `get_ticker()` | Real-time ticker for one contract |
| `get_all_tickers()` | Tickers for all contracts |
| `get_part_orderbook()` | Top 20 or 100 orderbook levels |
| `get_full_orderbook()` | Full L2 orderbook (auth required) |
| `get_trade_history()` | Recent trades |
| `get_klines()` | OHLCV candlestick data |
| `get_mark_price()` | Current mark price |
| `get_funding_rate()` | Current funding rate |
| `get_funding_history()` | Historical funding rates |
| `get_server_time()` | Server timestamp |
| `get_service_status()` | Exchange operational status |

### KucoinFuturesTrading

| Method | Description |
|--------|-------------|
| `add_order()` | Place a futures order |
| `add_order_test()` | Dry-run order validation |
| `add_order_batch()` | Place multiple orders |
| `cancel_order_by_id()` | Cancel by system ID |
| `cancel_order_by_client_oid()` | Cancel by client ID |
| `cancel_all()` | Cancel all open orders |
| `cancel_all_stop_orders()` | Cancel all stop orders |
| `get_order_by_id()` | Query order by system ID |
| `get_order_by_client_oid()` | Query order by client ID |
| `get_order_list()` | Paginated order list |
| `get_recent_closed_orders()` | Recent closed orders |
| `get_stop_orders()` | Untriggered stop orders |
| `get_fills()` | Paginated fill history |
| `get_recent_fills()` | Recent fills (24h) |
| `get_open_order_value()` | Open order statistics |
| `set_dcp()` | Set dead connection protection |
| `get_dcp()` | Query DCP settings |

### KucoinFuturesAccount

| Method | Description |
|--------|-------------|
| `get_account_overview()` | Balance, equity, margin summary |
| `get_position()` | Position for one symbol |
| `get_positions()` | All open positions |
| `get_positions_history()` | Historical closed positions |
| `get_margin_mode()` | Query margin mode |
| `set_margin_mode()` | Switch isolated/cross |
| `get_cross_margin_leverage()` | Query cross leverage |
| `set_cross_margin_leverage()` | Set cross leverage |
| `get_max_open_size()` | Max contracts openable |
| `get_max_withdraw_margin()` | Max withdrawable margin |
| `add_isolated_margin()` | Deposit margin to position |
| `remove_isolated_margin()` | Withdraw margin from position |
| `get_risk_limit()` | Risk limit tiers |
| `get_funding_history()` | Personal funding fee records |
