---
title: "Getting Started with kucoin"
author: "Dereck Mezquita"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with kucoin}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  results = "hold",
  comment = "#>"
)

box::use(
  kucoin[
    KucoinMarketData, KucoinTrading, KucoinAccount,
    KucoinStopOrders, KucoinOcoOrders, KucoinDeposit,
    KucoinSubAccount, get_api_keys
  ],
  lubridate[ymd_hms]
)

box::use(
  connectcore[local_mock_api],
  ../tests/testthat/mock_router[.mock_routes]
)

KEYS <- get_api_keys(
  api_key = "fake-key",
  api_secret = "fake-secret",
  api_passphrase = "fake-passphrase"
)
BASE <- "https://api.kucoin.com"

local_mock_api(.mock_routes)
```

This vignette demonstrates how to use `kucoin` in **synchronous** mode.

## Setup

```{r load}
box::use(
  kucoin[
    KucoinMarketData, KucoinTrading, KucoinAccount,
    KucoinStopOrders, KucoinOcoOrders, KucoinDeposit,
    KucoinSubAccount, get_api_keys
  ],
  lubridate[ymd_hms]
)

keys <- get_api_keys(
  api_key = "your-api-key",
  api_secret = "your-api-secret",
  api_passphrase = "your-api-passphrase"
)
```

```{r keys, echo = FALSE}
keys <- KEYS
base <- BASE
```

---

## Market Data

The `KucoinMarketData` class covers all public (no auth) market endpoints.

```{r market-init}
market <- KucoinMarketData$new()
```

```{r market-init-hidden, echo = FALSE}
market <- KucoinMarketData$new(keys = keys, base_url = base)
```

### Ticker

```{r ticker}
ticker <- market$get_ticker(symbol = "BTC-USDT")
ticker
```

### 24hr Statistics

```{r stats-24hr}
stats <- market$get_24hr_stats(symbol = "BTC-USDT")
stats
```

### All Tickers

```{r all-tickers}
tickers <- market$get_all_tickers()
tickers
```

### Trade History

```{r trade-history}
trades <- market$get_trade_history(symbol = "BTC-USDT")
trades
```

### Partial Orderbook

```{r orderbook}
book <- market$get_part_orderbook(symbol = "BTC-USDT", size = 20)
book
```

### Klines (Candlestick Data)

```{r klines}
klines <- market$get_klines(
  symbol = "BTC-USDT",
  timeframe = "15min",
  from = ymd_hms("2024-10-16 20:00:00"),
  to = ymd_hms("2024-10-16 21:00:00")
)
klines
```

### Currency Info

```{r currency}
btc <- market$get_currency(currency = "BTC")
btc
```

### Symbol Info

```{r symbol}
sym <- market$get_symbol(symbol = "BTC-USDT")
sym
```

---

## Trading

The `KucoinTrading` class manages HF spot orders. All trading endpoints
require authentication.

### Place a Test Order

Test orders validate parameters without executing:

```{r trading-test-order}
trading <- KucoinTrading$new()
```

```{r trading-init-hidden, echo = FALSE}
trading <- KucoinTrading$new(keys = keys, base_url = base)
```

```{r}
result <- trading$add_order_test(
  type = "limit",
  symbol = "BTC-USDT",
  side = "buy",
  price = "50000",
  size = "0.0001"
)
result
```

### Cancel an Order

```{r trading-cancel}
cancelled <- trading$cancel_order_by_id(order_id = "670fd33bf9406e0007ab3945", symbol = "BTC-USDT")
cancelled
```

### Query Open Orders

```{r trading-open-orders}
open_orders <- trading$get_open_orders(symbol = "BTC-USDT")
open_orders
```

---

## Stop Orders

```{r stop-orders}
stop <- KucoinStopOrders$new()
```

```{r stop-hidden, echo = FALSE}
stop <- KucoinStopOrders$new(keys = keys, base_url = base)
```

```{r}
result <- stop$add_order(
  type = "limit",
  symbol = "BTC-USDT",
  side = "sell",
  price = "60000",
  size = "0.0001",
  stop_price = "59000"
)
result
```

---

## OCO Orders

An OCO (One-Cancels-Other) order pairs a limit order with a stop-limit
order; when one side fills, the other is cancelled automatically.

```{r oco-orders}
oco <- KucoinOcoOrders$new()
```

```{r oco-hidden, echo = FALSE}
oco <- KucoinOcoOrders$new(keys = keys, base_url = base)
```

```{r}
result <- oco$add_order(
  symbol = "BTC-USDT",
  side = "sell",
  price = "110000",
  size = "0.0001",
  stop_price = "90000",
  limit_price = "89500"
)
result
```

---

## Account Management

### Account Summary

```{r account-summary}
account <- KucoinAccount$new()
```

```{r account-hidden, echo = FALSE}
account <- KucoinAccount$new(keys = keys, base_url = base)
```

```{r}
summary <- account$get_summary()
summary
```

### Spot Account Balances

```{r spot-accounts}
balances <- account$get_spot_accounts()
balances
```

---

## Deposits

### Get Deposit Addresses

```{r deposit-addresses}
deposit <- KucoinDeposit$new()
```

```{r deposit-hidden, echo = FALSE}
deposit <- KucoinDeposit$new(keys = keys, base_url = base)
```

```{r}
addrs <- deposit$get_deposit_addresses(currency = "USDT")
addrs
```

### Sync Orders and Modify

Sync variants return fill results in a single round trip:

```{r, eval = FALSE}
# Place order and get immediate fill result
order <- trading$add_order_sync(
  type = "limit", symbol = "BTC-USDT", side = "buy",
  price = "50000", size = "0.0001"
)
cat("Status:", order$status, "Filled:", order$deal_size, "\n")

# Modify an existing order's price
modified <- trading$modify_order(
  symbol = "BTC-USDT",
  order_id = order$order_id,
  new_price = "51000"
)
cat("New order ID:", modified$new_order_id, "\n")
```

### Dead Connection Protection (DCP)

A dead-man's switch that auto-cancels orders if your bot stops heartbeating:

```{r, eval = FALSE}
# Enable: cancel all BTC-USDT orders if no request in 30 seconds
trading$set_dcp(timeout = 30, symbols = "BTC-USDT")

# Check current DCP settings
dcp <- trading$get_dcp()
cat("Timeout:", dcp$timeout, "s\n")

# Disable
trading$set_dcp(timeout = -1)
```

---

## Fee Rates

```{r, eval = FALSE}
# Base fee rate (account tier default)
base_fees <- account$get_base_fee_rate()
cat("Base taker:", base_fees$taker_fee_rate, "\n")

# Per-symbol actual rates (after VIP/KCS discounts)
actual_fees <- account$get_fee_rate(symbols = "BTC-USDT,ETH-USDT")
actual_fees
```

## HF Trading Ledger

The HF ledger contains fills, fees, and settlements from HF orders (7-day window):

```{r, eval = FALSE}
hf_ledger <- account$get_hf_ledger(currency = "USDT", biz_type = "TRADE_EXCHANGE")
hf_ledger
```

## Server Time and Service Status

```{r, eval = FALSE}
# Check clock drift
st <- market$get_server_time()
drift_ms <- as.numeric(lubridate::now()) * 1000 - st$server_time
cat("Clock drift:", round(drift_ms), "ms\n")

# Pre-flight: is the exchange operational?
status <- market$get_service_status()
if (status$status != "open") stop("Exchange not operational: ", status$msg)
```

## Fiat Prices

```{r, eval = FALSE}
prices <- market$get_fiat_prices(base = "USD", currencies = "BTC,ETH,USDT")
prices
```

---

## Fund Transfers

Deposits land in the **main** account, but HF spot orders require funds in
the **trade** account. Use `KucoinTransfer` to move funds between account types.

```{r, eval = FALSE}
box::use(kucoin[KucoinTransfer])

transfer <- KucoinTransfer$new()

# Check how much USDT is available to transfer
balance <- transfer$get_transferable(currency = "USDT", type = "MAIN")
balance

# Transfer USDT from main to trade account
result <- transfer$add_transfer(
  client_order_id = "unique-id-here",
  currency = "USDT",
  amount = "100",
  type = "INTERNAL",
  from_account_type = "MAIN",
  to_account_type = "TRADE"
)
result
```

---

## Withdrawals

Use `KucoinWithdrawal` to check withdrawal limits, initiate withdrawals,
and monitor withdrawal status.

```{r, eval = FALSE}
box::use(kucoin[KucoinWithdrawal])

withdrawal <- KucoinWithdrawal$new()

# Check withdrawal quotas and fees
quotas <- withdrawal$get_withdrawal_quotas(currency = "USDT", chain = "trx")
quotas

# Withdraw USDT via TRC20
result <- withdrawal$add_withdrawal(
  currency = "USDT",
  to_address = "your-trc20-address",
  amount = "10",
  withdraw_type = "ADDRESS",
  chain = "trx"
)
result

# Check withdrawal history
history <- withdrawal$get_withdrawal_history(currency = "USDT")
history
```

---

## Sub-Account Management

### List Sub-Accounts

```{r sub-accounts}
sub <- KucoinSubAccount$new()
```

```{r sub-hidden, echo = FALSE}
sub <- KucoinSubAccount$new(keys = keys, base_url = base)
```

```{r}
subs <- sub$get_sub_account_list()
subs
```

---

## Clock Drift: Server Time Signing

By default, HMAC request signatures use your local machine's clock. If your
system time is out of sync with KuCoin's servers, authenticated requests may
fail. You can configure any class to fetch the server time before each
authenticated request:

```{r, eval = FALSE}
# Use server time for signing (adds one round trip per request)
trading <- KucoinTrading$new(time_source = "server")

# All authenticated calls now use the exchange clock
order <- trading$add_order_test(
  type = "limit", symbol = "BTC-USDT", side = "buy",
  price = "50000", size = "0.0001"
)
```

The `time_source` parameter is available on all class constructors:
`KucoinTrading`, `KucoinAccount`, `KucoinStopOrders`, `KucoinOcoOrders`,
`KucoinDeposit`, `KucoinTransfer`, `KucoinWithdrawal`, and `KucoinSubAccount`.

---

## Next Steps

- See `vignette("async-usage")` for promise-based asynchronous operation.
- See `vignette("margin-trading")` for margin trading, short selling, and lending.
- See `vignette("futures-trading")` for perpetual futures contracts.
- Browse the [pkgdown site](https://dereckscompany.github.io/kucoin/) for full method documentation.
- For bulk historical data downloads, see `?kucoin_backfill_klines`.
