---
title: "Margin Trading with kucoin"
author: "Dereck Mezquita"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Margin Trading with kucoin}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  results = "hold",
  comment = "#>"
)

box::use(
  kucoin[
    KucoinMarginTrading, KucoinMarginData, KucoinLending, get_api_keys
  ]
)

box::use(../tests/testthat/mock_router[mock_router])

KEYS <- get_api_keys(
  api_key = "fake-key",
  api_secret = "fake-secret",
  api_passphrase = "fake-passphrase"
)
BASE <- "https://api.kucoin.com"

options(httr2_mock = mock_router)
```

This vignette covers margin trading, lending, and margin market data using
the `kucoin` package. All examples assume synchronous usage.

## Overview

The package provides three classes for margin operations:

| Class | Purpose |
|-------|---------|
| `KucoinMarginTrading` | Open/close short and long positions, borrow, repay, manage leverage |
| `KucoinMarginData` | Query margin-enabled symbols, config, risk limits, collateral ratios |
| `KucoinLending` | Lend assets to earn interest, manage lending orders |

## Setup

```{r load}
box::use(
  kucoin[
    KucoinMarginTrading, KucoinMarginData, KucoinLending, get_api_keys
  ]
)

keys <- get_api_keys(
  api_key = "your-api-key",
  api_secret = "your-api-secret",
  api_passphrase = "your-api-passphrase"
)

margin <- KucoinMarginTrading$new(keys = keys)
margin_data <- KucoinMarginData$new(keys = keys)
lending <- KucoinLending$new(keys = keys)
```

```{r keys, echo = FALSE}
keys <- KEYS
base <- BASE
margin <- KucoinMarginTrading$new(keys = keys, base_url = base)
margin_data <- KucoinMarginData$new(keys = keys, base_url = base)
lending <- KucoinLending$new(keys = keys, base_url = base)
```

---

## Margin Trading

### Short Selling

Short selling lets you profit from a price decline. The package uses
intent-based methods that handle borrowing and repayment automatically:

```{r short}
# Open a short: borrows BTC and sells it
order <- margin$open_short(
  symbol = "BTC-USDT",
  size = 0.001
)
order

# Later, close the short: buys BTC back and repays the loan
close <- margin$close_short(
  symbol = "BTC-USDT",
  size = 0.001
)
close
```

### Leveraged Long

A leveraged long lets you buy more of an asset than your balance allows:

```{r long}
# Open a leveraged long: borrows USDT and buys BTC
order <- margin$open_long(
  symbol = "BTC-USDT",
  size = 0.001
)
order

# Later, close the long: sells BTC and repays the USDT loan
close <- margin$close_long(
  symbol = "BTC-USDT",
  size = 0.001
)
close
```

### Limit Orders

All four methods default to market orders. Use `type = "limit"` for limit
orders:

```{r limit}
order <- margin$open_short(
  symbol = "BTC-USDT",
  type = "limit",
  price = 100000,
  size = 0.001,
  timeInForce = "GTC"
)
order
```

### Cross vs Isolated Margin

By default, all methods use **cross margin** (shared collateral pool).
For **isolated margin** (risk limited to one pair), set `isIsolated = TRUE`:

```{r isolated}
order <- margin$open_short(
  symbol = "BTC-USDT",
  size = 0.001,
  isIsolated = TRUE
)
order
```

### Dry Run (Test Orders)

Validate parameters without placing a real order:

```{r dry-run}
test <- margin$open_short(
  symbol = "BTC-USDT",
  size = 0.001,
  dry_run = TRUE
)
test
```

### Client Order IDs

Track orders with your own identifiers:

```{r client-oid}
order <- margin$open_short(
  symbol = "BTC-USDT",
  size = 0.001,
  clientOid = "my-strategy-short-001"
)
order$client_oid
```

---

## Manual Borrow and Repay

The intent-based methods (`open_short`, `close_short`, etc.) handle
borrowing and repayment automatically. For advanced workflows where you
want explicit control:

```{r borrow-repay}
# Manually borrow USDT
loan <- margin$borrow(currency = "USDT", size = 1000)
loan

# ... do your trading ...

# Manually repay
result <- margin$repay(currency = "USDT", size = 1000)
result
```

### Borrow History and Interest

```{r history}
# Check borrow history
borrows <- margin$get_borrow_history(query = list(currency = "USDT"))
borrows

# Check repayment history
repays <- margin$get_repay_history(query = list(currency = "USDT"))
repays

# Check interest accrued
interest <- margin$get_interest_history(query = list(currency = "USDT"))
interest

# Current borrow rates
rates <- margin$get_borrow_rate(query = list(currency = "BTC,USDT,ETH"))
rates
```

### Leverage

```{r leverage}
# Set leverage multiplier
margin$modify_leverage(leverage = 5)
```

---

## Margin Market Data

Query margin-specific market information:

```{r margin-data}
# Available cross margin trading pairs
symbols <- margin_data$get_cross_margin_symbols()
symbols[, .(symbol, enable_trading)]

# Available isolated margin trading pairs
iso_symbols <- margin_data$get_isolated_margin_symbols()
iso_symbols[, .(symbol, max_leverage, trade_enable)]

# Global margin config
config <- margin_data$get_margin_config()
cat("Max leverage:", config$max_leverage, "\n")
cat("Liquidation debt ratio:", config$liq_debt_ratio, "\n")

# Collateral ratios
ratios <- margin_data$get_collateral_ratio()
ratios
```

```{r risk-limit}
# Risk limits (requires auth)
limits <- margin_data$get_risk_limit(isIsolated = FALSE)
limits[, .(currency, borrow_max_amount, borrow_enabled)]
```

---

## Lending

Earn passive income by lending your assets to the margin lending pool:

```{r lending}
# Check available lending currencies
market <- lending$get_loan_market()
market

# Check market interest rates (last 7 days)
rates <- lending$get_loan_market_rate(currency = "USDT")
rates

# Lend 1000 USDT at 5% interest
order <- lending$purchase(currency = "USDT", size = 1000, interestRate = 0.05)
order$order_no

# Update the interest rate
lending$modify_purchase(
  currency = "USDT",
  purchaseOrderNo = order$order_no,
  interestRate = 0.06
)

# Check your lending orders
orders <- lending$get_purchase_orders(query = list(currency = "USDT", status = "DONE"))
orders

# Redeem (withdraw) lent assets
result <- lending$redeem(
  currency = "USDT",
  size = 500,
  purchaseOrderNo = order$order_no
)
result$order_no

# Check redemption history
redeems <- lending$get_redeem_orders(query = list(currency = "USDT", status = "DONE"))
redeems
```

---

## Method Reference

### KucoinMarginTrading

| Method | Description |
|--------|-------------|
| `open_short()` | Borrow + sell (profit from price decline) |
| `close_short()` | Buy back + repay (close a short position) |
| `open_long()` | Borrow + buy (leveraged long) |
| `close_long()` | Sell + repay (close a leveraged long) |
| `borrow()` | Manually borrow assets |
| `repay()` | Manually repay borrowed assets |
| `get_borrow_history()` | Query borrow records |
| `get_repay_history()` | Query repayment records |
| `get_interest_history()` | Query interest accrual history |
| `get_borrow_rate()` | Current borrow interest rates |
| `modify_leverage()` | Update leverage multiplier |

### KucoinMarginData

| Method | Description |
|--------|-------------|
| `get_cross_margin_symbols()` | Cross margin trading pairs |
| `get_isolated_margin_symbols()` | Isolated margin trading pairs |
| `get_margin_config()` | Global margin config (leverage, ratios) |
| `get_collateral_ratio()` | Collateral ratio tiers |
| `get_risk_limit()` | Borrow/hold limits per currency |

### KucoinLending

| Method | Description |
|--------|-------------|
| `get_loan_market()` | Available lending currencies |
| `get_loan_market_rate()` | Market interest rate history |
| `purchase()` | Lend assets to earn interest |
| `modify_purchase()` | Update lending interest rate |
| `get_purchase_orders()` | Query lending orders |
| `redeem()` | Withdraw lent assets |
| `get_redeem_orders()` | Query redemption orders |
